Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-13 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
implement Stepan's comments
Advance adhoc response for incoherent

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{red}{Should we keep it then? }

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{For this specific purpose, we applied four dimensional 
      binning to our incoherent DVCS data to get kinematical mean values close 
      to the published free proton results. The review committee members are 
      invited to check our kinematical distributions in 
      fig.~\ref{fig:incoh-kin} for the shown bins in FIG.~6 in the PRL and the 
      free proton data highlighted in figure \ref{fig:free-p}. }

@@

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{We have studied this effect in details. The review 
      committee members are invited to check appendix H in the analysis note 
      \url{ 
      https://www.jlab.org/Hall-B/shifts/index.php?display=admin&task=paper_review&rid=7619165&operation=view}.}

\item  There is also no mention of final state interactions in the paper. It is 
   not obvious to me that the FSA should be zero for a beam spin asymmetry on 
      4He. If you have a calculation that shows this is the case, it would be 
      good to mention it.\\
   \textcolor{blue}{There are no such theoretical calculations of the FSI on 
      the incoherent DVCS asymmetries on the $^4$He. }

>>>>

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{blue}{The text is updated.}

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{For this specific purpose, we applied four dimensional 
      binning to our incoherent DVCS data to get kinematical mean values close 
      to the published free proton results. The review committee members are 
      invited to check our kinematical distributions in 
      fig.~\ref{fig:incoh-kin} for the shown bins in FIG.~6 in the PRL and the 
      free proton data highlighted in figure \ref{fig:free-p}. }
      \textcolor{red}{Figure provided are not corresponding. Moreover, we talk 
      about extrapolating free proton data in the paper. Yet, it appears 
      that we are rather rebinning the eg6 data. We should update figures
      (including in the analysis note) and rephrase the statement in the 
      paper.}

@@

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{We have studied this effect, we updated the paper to
      address the question. The review 
      committee members are invited to check appendix H in the analysis note 
      for more details
      \url{ 
      https://www.jlab.org/Hall-B/shifts/index.php?display=admin&task=paper_review&rid=7619165&operation=view}.}
   \textcolor{red}{Please Mohammad check what I added in the paper on this topic.}

\item  There is also no mention of final state interactions in the paper. It is 
   not obvious to me that the FSA should be zero for a beam spin asymmetry on 
      4He. If you have a calculation that shows this is the case, it would be 
      good to mention it.\\
   \textcolor{blue}{There are no such theoretical calculations of the FSI on 
      the incoherent DVCS asymmetries on the $^4$He. A statement has been added
      toward the end to address this point.}

### 2018-08-13 eg6-letters/incoherent/incoherent_prl.tex
Advance adhoc response for incoherent

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional imaging of partons within the generalized parton 
distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the scattering is off the entire nucleus, which is 
left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
nucleon, which is ejected from the nucleus.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
proton at rest, was required to be greater than a minimum allowed value at 
given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
We also rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from  CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring a form of EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, while our experiment shows no sign 
of an increase of ratios. This measurement shows that an important nuclear 
effect is missing from the existing models in order to explain this strong 
quenching of the BSA.

>>>>

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional imaging of partons within the generalized parton 
distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the scattering is off the entire nucleus, which is 
left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
nucleon, which is ejected from the nucleus.
The latter is the focus of this letter and provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
proton at rest, was required to be greater than a minimum allowed value at 
given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring the EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, while our experiment shows no sign 
of an increase of ratios. This measurement shows that an important nuclear 
effect is missing from the existing models in order to explain this strong 
quenching of the BSA. More theoretical developments will be needed to identify 
the origin of this quenching, in particular it will be key to differenciate 
initial from final state effects and how they can affect the DVCS assymetries.
